---
title: "WriteUp"
output: html_document
---
Dataset from
Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, 
H. Qualitative Activity Recognition of Weight Lifting Exercises. 
Proceedings of 4th International Conference in Cooperation with 
SIGCHI (Augmented Human '13) . Stuttgart, Germany: ACM SIGCHI, 2013.
Read more: http://groupware.les.inf.puc-rio.br/har#ixzz3uJG8yOEC


Begin by providing remote urls to get the data from and setting working directory 
```{r}
train_url = "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
test_url = "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv" 

directory = "."
setwd(directory)
trainfile = "train.csv"
testfile = "test.csv"
train_dest = paste(directory, trainfile,sep ="/")
test_dest = paste(directory, testfile,sep ="/")
# if files do not exist then download them from url
if (!file.exists(train_dest) | !file.exists(test_dest)){
method = "curl"  
download.file(train_url,destfile = train_dest,method = method)
download.file(test_url,destfile = test_dest,method = method)
}
```
Read in "raw" datasets

```{r}
train_raw <- read.csv(train_dest)
test_raw <-read.csv(test_dest)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
